---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# volcano

<!-- badges: start -->
<!-- badges: end -->

The goal of volcano is to georeference the `volcano` data set. 

## Installation

You can install the development version of volcano from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/volcano")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(volcano)
## basic example code
image(volc, asp = 1)

(vtiff <- terra::rast(system.file("extdata/volcano.tif", package = "volcano", mustWork = TRUE)))
terra::contour(vtiff, add = TRUE)
```


See the vignette for more. 


## Code of Conduct
  
Please note that the volcano project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
