---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# volcano

<!-- badges: start -->
<!-- badges: end -->

The goal of volcano is to georeference the `volcano` data set. There are 3 datasets 

- `volc` volcano matrix in an R xyz 'image' list, oriented correctly for use with raster tools
- `volc_extent` the four number extent `c(xmin, xmax, ymin, ymax)`
- `volc_proj` the projection string, it's an EPSG code for NZMG


## Installation

You can install the development version of volcano from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/volcano")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(volcano)

print(volc_extent)
print(volc_proj)
diff(volc_extent)[c(1, 3)]  ## Ross Ihaka's famous digitization was 10m pixels
## basic example code
image(volc, asp = 1)

(vtiff <- terra::rast(system.file("extdata/volcano.tif", package = "volcano", mustWork = TRUE)))
terra::contour(vtiff, add = TRUE)
```


`volc` is just volcano stored as a `image()` list. We can work directly with it by reversing each axis, and using GDAL to get other data in the same projection. 

```{r}
#remotes::install_github(file.path("hypertidy", c("whatarelief", "ximage")))
prj <- "EPSG:27200"
oriented <- volcano[nrow(volcano):1, ncol(volcano):1]

ximage::ximage(oriented, extent = volc_extent, asp = 1)

x <- whatarelief::elevation(volc_extent, dimension = c(256, 256), projection = volc_proj)
im <- whatarelief::imagery(volc_extent, dimension = c(512, 512), projection = volc_proj)
ximage::ximage(im, extent = volc_extent, add = TRUE)
ximage::xcontour(x, extent = volc_extent, add = T, col = "white")


```



## Code of Conduct
  
Please note that the volcano project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
