---
title: "volcano-georef"
output:
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 7
vignette: >
  %\VignetteIndexEntry{volcano-georef}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



Before we start, what's the answer?

```R
oriented <-volcano[nrow(volcano):1,ncol(volcano):1]

extent <- c(2667394, 2668004, 6478902, 6479772)
projection <- "+proj=nzmg +datum=WGS84"
terra::rast(oriented, extent = extent, crs = projection)
class       : SpatRaster 
dimensions  : 87, 61, 1  (nrow, ncol, nlyr)
resolution  : 10, 10  (x, y)
extent      : 2667394, 2668004, 6478902, 6479772  (xmin, xmax, ymin, ymax)
coord. ref. : +proj=nzmg +lat_0=0 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs 
source      : memory 
name        : lyr.1 
min value   :    94 
max value   :   195 
```

Now, what are we talking about. :)


## R's volcano data set

The volcano data set in R is ungeoreferenced, and `image()` is also weird. 

```{r image}
image(volcano)


image(seq(0, ncol(volcano)), seq(0, nrow(volcano)), t(volcano[,ncol(volcano):1]), asp = 1)
```

But, good authority has it that `c(2667704 6479092)` is the x,y coordinate of the highest point in New Zealand Map Grid, and the documentation tells us that the data set has 10m cells.  

```{r volcano}
prj <- "+proj=nzmg +datum=WGS84"
maxnz <- cbind(2667704, 6479092)
library(terra)
r <- rast(volcano[nrow(volcano):1,ncol(volcano):1])
plot(r, asp = 1)  ## terra at least has good defaults 
## which cell has the highest point
wm <- which.max(values(r))
xmn <- maxnz[1,1] - 10 * terra::colFromCell(r, wm)
xmx <- maxnz[1,1] + 10 * (ncol(r) - colFromCell(r, wm))
ymn <- maxnz[1,2] - 10 * (nrow(r) - rowFromCell(r, wm))
ymx <- maxnz[1,2] + 10 * rowFromCell(r, wm)
volc <- set.ext(r, ext(xmn, xmx, ymn, ymx))

crs(volc) <- prj
plot(volc)
```


We good. Actually let's check. 


```{r setup}
library(gdalio)
source(gdalio_format_source())

```


```{r sources}
src <- gdalio_sources() |> dplyr::distinct()
gdalio_set_default_grid(volc)

elev <- dplyr::filter(src, name == "aws-elevation-tiles-prod")
plot(gdalio_terra(elev$source, resample = "cubic"))
```


Let's go for better resolution. 

```{r}
grd <- gdalio_get_default_grid()
grd$dimension <- grd$dimension * 10 ## 1m
gdalio_set_default_grid(grd)
print(grd$dimension)
plot(gdalio_terra(elev$source, resample = "cubic"))
```

```{r esri}
wi <- dplyr::filter(src, grepl("WorldImagery", name)) 
plotRGB(gdalio_terra(wi$source[1], resample = "cubic", bands = 1:3))

```



```{r osm}
osm <- dplyr::filter(src, grepl("wms_openstreetmap_tms", name)) 
plotRGB(gdalio_terra(osm$source[1], resample = "cubic", bands = 1:3))
```

```{r goog}
gm <- dplyr::filter(src, grepl("wms_googlemaps_tms", name)) 
plotRGB(gdalio_terra(gm$source[1], resample = "cubic", bands = 1:3))
```

Do we really believe it!

```{r contour}
plotRGB(gdalio_terra(wi$source[1], resample = "cubic", bands = 1:3))
contour(volc, add = TRUE)
```


```{r contour2}
plotRGB(gdalio_terra(wi$source[1], resample = "cubic", bands = 1:3))
contour(gdalio_terra(elev$source, resample = "cubic"), add = TRUE)
```
